---
title: "The Causeway Coast Way, NI"
author: "Connor Claypool"
date: "26 July 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This map is a demo of `leaflet` for interactive mapping in R, and shows some of the main points of interest on or near the Causeway Coast Way, a popular walking trail in Northern Ireland. Clicking a marker reveals the name of that specific location.

```{r, fig.width=10, message=FALSE, echo=FALSE}

cc <- data.frame(
    lat = c(55.200645,
            55.299015,
            55.239573,
            55.240282,
            55.238393,
            55.241193,
            55.215755,
            55.210764,
            55.205426,
            55.185117
            ),
    lng = c(-6.250119,
            -6.206728,
            -6.332456,
            -6.367019,
            -6.448212,
            -6.511899,
            -6.544450,
            -6.579662,
            -6.657812,
            -6.719142
            ),
    popup = c("The Diamond, Ballycastle",
              "Rathlin Island",
              "Carrick-a-Rede Rope Bridge",
              "Ballintoy Parish Church",
              "Dunseverick Castle",
              "Giant's Causeway",
              "Bayview Hotel, Portballintrae",
              "Dunluce Castle",
              "Portrush Harbour",
              "The Promenade, Portstewart")
)

library(dplyr)
library(leaflet)
cc %>% leaflet() %>% addTiles() %>% addMarkers(popup = ~popup)